Essays in Computational Management Science

### 2018-05-21 Chapters/Chapter01.tex
Typos typos...

As there are no miners, there are also no fees, which is a major incentive to newcomers. Tokens may be freely transfered without any loses, even for tiny amounts, enabling micropayments. For example, online workers paid per hour may receive their payments every hour, reducing the default risk. This allows untrusted parties to work together reducing the risk for both. The contractor always wants to pay in the end, while the workers always wants to get paid in the beginning.

@@

Simulator's random variables simulator are all sampled from their distributions. The time between two transactions is sampled from an exponential distribution with $\lambda_\text{TX}$. The number of attempts to find a solution of the proof-of-work is sampled from a geometric distribution with $p=2^{w}$, where $w$ can be either $w_\text{TX}$ or $w_\text{block}$. The amount of time spent to solve the proof-of-work is calculated dividing the number of attempts by the hash rate of the device (which could be either a miner or an user). The time between blocks is just the amount of time spent to solve the proof-of-work with $w_\text{block}$.

@@

First, two simulations in the extreme cases: (i) no miners, (ii) no transactions. The first should have precisely the same behavior as Bitcoin's blocks with one block after the other forming a long chain. The latter should have a similar behavior as Iota's, forming a Direct Acyclic Graph (DAG) with new transactions confirming previous ones. We can see in Figure \ref{fig:hathor-similarities} that both cases seem to be correct.

@@

When $\lambda_\text{TX} \rightarrow 0$, the number of tips goes towards one. The explanation is that there will be only one new transaction solving the proof-of-work per turn. So, new transactions will always confirm two tips, reducing the number of tips by one---each transaction confirms two tips and create one new one, hence the balance is -1. As it is impossible to have less to have less than one tip, it converges to one.

@@

In Figure \ref{fig:hathor-network-validated}, we can see how long it takes for a transaction to be network validated in different scenarios. The time is quite the same for $\lambda_\text{TX}$ below than one, but it changes for higher values.

It is interesting to notice that there is a trade-off when $\lambda_\text{TX}$ increases. On the one hand, new transactions grow the DAG and accelerate the network validation, whereas, on the other hand, both the number of tips and the width of the swarm increases, dispercing this acceleration. The results show that, in fact, the time to be network validated increases with $\lambda_\text{TX}$.

>>>>

As there are no miners, there are also no fees, which is a major incentive to newcomers. Tokens may be freely transferred without any losses, even for tiny amounts, enabling micropayments. For example, online workers paid per hour may receive their payments every hour, reducing the default risk. This allows untrusted parties to work together reducing the risk for both. The contractor always wants to pay in the end, while the workers always wants to get paid in the beginning.

@@

Simulator's random variables are all sampled from their distributions. The time between two transactions is sampled from an exponential distribution with $\lambda_\text{TX}$. The number of attempts to find a solution of the proof-of-work is sampled from a geometric distribution with $p=2^{w}$, where $w$ can be either $w_\text{TX}$ or $w_\text{block}$. The amount of time spent to solve the proof-of-work is calculated dividing the number of attempts by the hash rate of the device (which could be either a miner or an user). The time between blocks is just the amount of time spent to solve the proof-of-work with $w_\text{block}$.

@@

First, two simulations in the extreme cases: (i) no transactions, (ii) no miners. The first should have precisely the same behavior as Bitcoin's blocks with one block after the other forming a long chain. The latter should have a similar behavior as Iota's, forming a Direct Acyclic Graph (DAG) with new transactions confirming previous ones. We can see in Figure \ref{fig:hathor-similarities} that both cases seem to be correct.

@@

When $\lambda_\text{TX} \rightarrow 0$, the number of tips goes towards one. The explanation is that there will be only one new transaction solving the proof-of-work per turn. So, new transactions will always confirm two tips, reducing the number of tips by one---each transaction confirms two tips and create one new one, hence the balance is -1. As it is impossible to have less than one tip, it converges to one.

@@

In Figure \ref{fig:hathor-network-validated}, we can see how long it takes for a transaction to be network validated in different scenarios. The time is quite the same for $\lambda_\text{TX}$ less than one, but it changes for higher values.

It is interesting to notice that there is a trade-off when $\lambda_\text{TX}$ increases. On the one hand, new transactions grow the DAG and accelerate the network validation, whereas, on the other hand, both the number of tips and the width of the swarm increases, dispersing this acceleration. The results show that, in fact, the time to be network validated increases with $\lambda_\text{TX}$.
